
# Basic Plots

## Data

If you do not have your own data, you can use one of the pre-loaded R data availables.

::: infonote
* The command data() would display the available pre-loaded data
* The command data(name-of-data) would load the data frame into your R environment
* The command ?name-of-data would display a description of the data
:::

In this document we used the **iris** data, the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. 

```{r results='asis'}
data("iris")
knitr::kable(head(iris), format="markdown")
```


## Plotting

First, we need to select the **data** to be used and which fields are to be used in the plot in the aesthetic area.

```{r}
#Empty plot
#p <- ggplot()
#p
#Data to be used
#p <- ggplot(data=diamonds)
#p
#Indicating axis
p <- ggplot(data=diamonds, aes(x = carat, y = price)) 
p
```

### Geometric {.tabset .tabset-pill}

Secondly, we have to choose which kind of plot we want

#### Scatter plot

```{r}
p <- ggplot(data = iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point()
p
```

#### Box plot

```{r}
p <- ggplot(data = iris, aes(x = Species, y = Petal.Length)) + geom_boxplot()
p
```

#### Violin plot

```{r}
p <- ggplot(data = iris, aes(x = Species, y = Petal.Width)) + geom_violin()
p
```


#### Density plot

```{r}
p <- ggplot(data = iris, aes(x = Sepal.Length)) + geom_density()
p
```

#### Histogram plot

```{r warning=FALSE, message=FALSE}
p <- ggplot(data = iris, aes(x = Petal.Length)) + geom_histogram()
p
```

